Supplemental Information:\\ Harnessing Design Principles from Glass Sponges for Structurally Robust Lattice Structures

### 2018-10-01 Supplemental-FernandesWeaverBertoldi_AdvMaterials_2018.tex
.

For all buckling analysis, we performed a linear stability buckling analysis \KB{did you use *buckling or *frequency? Did you account for the effect of pre-deformation}
\KB{Since buckling may alter the periodicity of the
structure, we considered super cells consisting of $m \times n$
undeformed RVEs subjected to periodic boundary
conditions and calculated the critical strain for each of
them. The critical strain of the infinite periodic structure is
then defined as the minimum critical strain on all considered
super cells. \KB{it would be good to add this plot for each Design. Similar to Fig. 2c in "Complex Ordered Patterns in Mechanical Instability Induced Geometrically
Frustrated Triangular Cellular Structures"}}

\KB{how do you account for different $\theta$?}

\KB{comment on the results}

@@

\begin{figure}[H]
    \centering
	\includegraphics[width=0.6\linewidth]{SFig10.png}
	\caption{{\bf RVE used for the different designs.} This figure portrays the different RVEs used for the different designs considered. Each unit cell is shifted by half of a square cell to the horizontally and half of a square cell  vertically. Periodic boundary conditions are applied on the nodes that intersect with the light gray dashed line.}
	\label{RVE}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uniaxial loading condition. The color of each point on the graph corresponds to the optimum value of mass ratio for that particular number of diagonals. Four deformation plots of the optimum structure and buckling modes are provided on the right for their respective number of diagonals.}
    \label{BucklingOptimization}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.6\linewidth]{SFig7.pdf}
	\caption{{\bf Circular Cross Section Results.} The color of the lines correspond to it's respective design color below the plots. (a) Shows the linear elastic stiffness of the different designs as a function of the loading angle. All structures except for the design without diagonal reinforcement have the same stiffness. (b) Shows the critical buckling strain for varying loading angle. For all angles, Design A outperforms other diagonally reinforced designs. These results show that the two diagonal benefit persists beyond a particular beam cross-section design.}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig8.pdf}
	\caption{{\bf Rectangular Cross Section Parameter Exploration.} For each of these plots, we vary a single parameter while maintaining the base sponge inspired geometry constant. The gray line indicates the sponge design parameter. (a) Shows the critical buckling strain for varying spacing between diagonals. (b) Shows the structural stiffness of the geometry as we vary the mass ratio $\lambda$. (c) Shows the critical buckling strain of the geometry as we vary the mass ratio $\lambda$.}
	\label{SquareCrossSectionParameter}
\end{figure}

@@

\begin{figure}[H]
	\centering
	\includegraphics[width=0.9\linewidth]{SFig9.pdf}
	\caption{{\bf Circular Cross Section Parameter Exploration.} For each of these plots, we vary a single parameter while maintaining the base sponge inspired geometry constant. The gray line indicates the sponge design parameter. (a) Shows the critical buckling strain for varying spacing between diagonals. (b) Shows the structural stiffness of the geometry as we vary the mass ratio $\lambda$. (c) Shows the critical buckling strain of the geometry as we vary the mass ratio $\lambda$.}
	\label{CircularCrossSectionParameter}
\end{figure}

>>>>

For all buckling analysis, we performed a linear stability buckling analysis ({\tt *Buckling} command in ABAQUS input file). We perform this analysis for varying angles $\theta$ and extract the first mode critical buckling strain. Since buckling may alter the periodicity of the
structure, we considered super cells consisting of $M \times M$
undeformed RVEs subjected to periodic boundary
conditions and calculated the critical strain for each of
them. The critical strain of the infinite periodic structure is
then defined as the minimum critical strain on all considered
super cells.

\KB{it would be good to add this plot for each Design. Similar to Fig. 2c in "Complex Ordered Patterns in Mechanical Instability Induced Geometrically
Frustrated Triangular Cellular Structures"} \mf{Yes, I like this plot and will work on creating it.}

From the main article figure\#\# \mf{add reference to main article results figure} we conclude that for all $\theta$, Design A provides a higher overall buckling strength over the other compared designs, while not compromising it's overall stiffness in every direction.

@@

\begin{figure}
    \centering
	\includegraphics[width=0.6\linewidth]{SFig10.png}
	\caption{{\bf RVE used for the different designs.} This figure portrays the different RVEs used for the different designs considered. Each unit cell is shifted by half of a square cell to the horizontally and half of a square cell  vertically. Periodic boundary conditions are applied on the nodes that intersect with the light gray dashed line.}
	\label{RVE}
\end{figure}

@@

\begin{figure}
    \centering
    \includegraphics[width=0.9\linewidth]{SFig6.png}
    \caption{{\bf Buckling Optimization.} Graph shows optimal value of critical buckling strain for varying number of diagonals. For all simulations, the total mass of the structure is maintained constant while the mass-ratio is allowed to vary. Furthermore, the diagonal separation for each pair of diagonal is allowed to vary together ensuring half symmetry of the structure at all times. The optimization is run under a uniaxial loading condition. The color of each point on the graph corresponds to the optimum value of mass ratio for that particular number of diagonals. Four deformation plots of the optimum structure and buckling modes are provided on the right for their respective number of diagonals.}
    \label{BucklingOptimization}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.6\linewidth]{SFig7.pdf}
	\caption{{\bf Circular Cross Section Results.} The color of the lines correspond to it's respective design color below the plots. (a) Shows the linear elastic stiffness of the different designs as a function of the loading angle. All structures except for the design without diagonal reinforcement have the same stiffness. (b) Shows the critical buckling strain for varying loading angle. For all angles, Design A outperforms other diagonally reinforced designs. These results show that the two diagonal benefit persists beyond a particular beam cross-section design.}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{SFig8.pdf}
	\caption{{\bf Rectangular Cross Section Parameter Exploration.} For each of these plots, we vary a single parameter while maintaining the base sponge inspired geometry constant. The gray line indicates the sponge design parameter. (a) Shows the critical buckling strain for varying spacing between diagonals. (b) Shows the structural stiffness of the geometry as we vary the mass ratio $\lambda$. (c) Shows the critical buckling strain of the geometry as we vary the mass ratio $\lambda$.}
	\label{SquareCrossSectionParameter}
\end{figure}

@@

\begin{figure}
	\centering
	\includegraphics[width=0.9\linewidth]{SFig9.pdf}
	\caption{{\bf Circular Cross Section Parameter Exploration.} For each of these plots, we vary a single parameter while maintaining the base sponge inspired geometry constant. The gray line indicates the sponge design parameter. (a) Shows the critical buckling strain for varying spacing between diagonals. (b) Shows the structural stiffness of the geometry as we vary the mass ratio $\lambda$. (c) Shows the critical buckling strain of the geometry as we vary the mass ratio $\lambda$.}
	\label{CircularCrossSectionParameter}
\end{figure}
